Subject-specific curves for time series forecasting of smart meter demand

### 2020-03-29 sscts-paper-1-wp.Rmd
Update feature selection section. Add note about improving feature selection for mixed effects models.

We use the pooled linear regression model for feature selection as it is quick to fit using ordinary least squares and allows us to model buildings by using a dummy variable for each. Using a linear model also has the advantage of allowing us to efficiently compute the leave-one-out cross-validation (LOOCV) scores using [@Seber2012-gu]

@@

>>>>

We use the pooled linear regression model for feature selection as it is quick to fit using OLS and allows us to model buildings by using a dummy variable for each. Using a linear model also has the advantage of allowing us to efficiently compute the leave-one-out cross-validation (LOOCV) scores using [@Seber2012-gu]

@@

It should be noted that feature selection could be further improved for the mixed effects models by proceeding with a step-wise selection process after the above process has completed for the pooled model. Features can be added or removed based on if an appropriate out of sample accuracy score improves. This allows us to benefit from the relative speed of fitting via OLS before further fine-tuning with a greedy selection algorithm.
